Text embedding models yield high-resolution insights into conceptual knowledge from short multiple-choice quizzes

### 2025-02-21 paper/main.tex
multiple choice -> multiple-choice

Our work makes several contributions to the study of how people acquire
conceptual knowledge. First, from a methodological standpoint, our modeling
framework provides a systematic means of mapping out and characterizing
knowledge in maps that have infinite (arbitrarily many) numbers of coordinates,
and of ``filling out'' those maps using relatively small numbers of multiple
choice quiz questions. Our experimental finding that we can use these maps to
predict responses to held-out questions has several psychological implications
as well. For example, concepts that are assigned to nearby coordinates by the
text embedding model also appear to be ``known to a similar extent'' (as
reflected by participants' responses to held-out questions;
Fig.~\ref{fig:predictions}). This suggests that participants also
\textit{conceptualize} similarly the content reflected by nearby embedding
coordinates. How participants' knowledge falls off with spatial distance is
captured by the knowledge maps we infer from their quiz responses
(e.g., Figs.~\ref{fig:smoothness},~\ref{fig:knowledge-maps}). In other words,
our study shows that knowledge about a given concept implies knowledge about
related concepts, and we also show how estimated knowledge falls off with
distance in text embedding space.

>>>>

Our work makes several contributions to the study of how people acquire
conceptual knowledge. First, from a methodological standpoint, our modeling
framework provides a systematic means of mapping out and characterizing
knowledge in maps that have infinite (arbitrarily many) numbers of coordinates,
and of ``filling out'' those maps using relatively small numbers of 
multiple-choice quiz questions. Our experimental finding that we can use these 
maps to predict responses to held-out questions has several psychological 
implications as well. For example, concepts that are assigned to nearby 
coordinates by the text embedding model also appear to be ``known to a similar 
extent'' (as reflected by participants' responses to held-out questions;
Fig.~\ref{fig:predictions}). This suggests that participants also
\textit{conceptualize} similarly the content reflected by nearby embedding
coordinates. How participants' knowledge falls off with spatial distance is
captured by the knowledge maps we infer from their quiz responses
(e.g., Figs.~\ref{fig:smoothness},~\ref{fig:knowledge-maps}). In other words,
our study shows that knowledge about a given concept implies knowledge about
related concepts, and we also show how estimated knowledge falls off with
distance in text embedding space.
